\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Final Project Log}
\author{Lab2, Group3}
\date{April 12, 2020}

\begin{document}

\maketitle

\section{Project Proposal}

\textbf{Assigned roles: }
\begin{itemize} 
	\item Jiwoo - Abstract, input/output and proposed solutions, 
	\item Jennie - Project plan
	\item Zoe - Objective
	\item Cynthia - Motivation
	\item Jeehyun - Algorithmic challenges
\end{itemize} 

\textbf{Comment on progress and meeting qualities:} \\
We met up one day in a study room and worked on it together. Since we were working on it together and can communicate to each other right away, our work progress was very efficient.

\section{Presentation}
Everyone made slides on what they worked on for the proposal. Again, very efficient because we sat down and made the powerpoint together on same day same place. Also practiced presenting couple times together with timer. We were proud that we finished right in the 10 min mark. 

\section{Requirement Specification}
\textbf{Assigned roles: }
\begin{itemize} 
	\item Jiwoo - Domains
	\item Jennie - UML diagram
	\item Zoe - Functional requirements
	\item Cynthia - Requirements for development and maintenance process
	\item Jeehyun - Non functional requirements
\end{itemize} 


\section{Design Specification}

Mainly done by Jiwoo while teammates were finishing up their part for search bar and adding logo to MajorSortActivity.java

\section{Meetings}

\begin{itemize} 
	\item Feb 6 - Started project.
	\item Feb 7 - Finished project proposal and submitted.
	\item Feb 13 - Submitted ppt.
	\item Mar 7 - Submitted requirement specification.
	\item Mar 23 - Each of us were assigned 4 universities and collected data in csv format.
	\item April 3 - Setup the basic outline for android project, wrote functions to retrieve data from csv files. Also implemented UI for first page. Added a bottom navigation bar with three options.
	\item April 5 - Changed csv files to change admission average from string to int (mid 80 to 85). Changed UI design for the first page. The bottom navigation bar is cancelled, instead we added a button called search by major. Adjusted second page and third page design.
	\item April 7 - Implemented second page scroll view, added a search bar.
	\item April 8 - Implemented searching/sorting algorithm, implemented third page list view. Changed search bar on second page to list view for better user experience.
	\item April 9 - Added coop/tuition/international/sorting options (ranking, admission average, tuition) in MajorSortActivity.java. Meet for about twelve hours and made a huge progress.
	\item April 10 - Finished up search bar and beautified interfaces.
	\item April 11 - Wrap up project, make detailed adjustments. Finish documentation. Created junit test files.
	\item April 12 - Export as eclipse project and submit.
	
\end{itemize}

\end{document}

